Assignment 2

### 2019-06-29 ex2/report/report.tex
Add Deep Learning section to the LaTeX file

\subsection{Deep Learning}
\subsection{Random Forests}
In addition to deep learning we trained a random forest classifier to detect attacks in network traffic.

>>>>

\subsection{Deep Learning}
We used PyTorch to build a neural network classifier. For this we used 5 fully connected layers with 512 neurons each and applied ReLU after each layer as well as dropout with a probability of 0.2. We use the binary cross entropy loss function for the classification task itself.

\subsection{Random Forests}
In addition to deep learning we trained a random forest classifier to detect attacks in network traffic.
